Manuscript drafts

### 2020-03-03 datasets/data_preprocessing.Rmd
Methods
- add information on simulation

## nudging dataset 
```{r}
# by Rosanna Nagtegaal
nudging <- template
nudging["paper", ] <- c(2006, 377, 100) 
```

@@

>>>>

## ace dataset 
## nudging dataset 
```{r}
# by Rosanna Nagtegaal
nudging <- template
nudging["paper", ] <- c(2006, 377, 100) 
```

@@

## wilson

# Save descriptive statistics

```{r eval = FALSE}
# put everything together in list. 
all <- list(ace = ace,
            nudging = nudging,
            ptsd = ptsd,
            software = software,
            wilson = wilson)

# save datafile, to serve as data for descriptive table in manuscript
save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
```

### 2020-03-03 manuscript/drafts/manuscript.Rmd
Methods
- add information on simulation

pathRdata <- "../../R/data/"

@@

\newpage
# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate.

@@

@@

#### ptsd
The review [@vandeSchoot2018]
The data [@Winter2020]

@@

## Models 
Five different models were applied on the data.

Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

####

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets. 
#### ACE
The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

@@

## Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
### Outcomes 
For each model, 
Several metrics are used to compare performance of different models over datasets,

>>>>

#pathRdata <- "../../R/data/"
pathRdata <- "data/"

@@

## active learning for systematic reviews 
achine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

\newpage
# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview?

@@

#### ace
The ACEInhibitors dataset from the study by [@Cohen2006].
The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.

a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

@@

#### ptsd
A review [@vandeSchoot2018] on longitudinal studies on posttraumatic stress symptoms assessed after exposure to trauma. 
The corresponding dataset [@Winter2020].

@@

## Simulations
The original systematic review is reproduced using five different models.

A simulation consists of the following elements:
we have a model $M$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$.

for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

@@

### Outcomes 
For each model, 
Several metrics are used to compare performance of different models over datasets,
